---
title: "P8105_HW1_hw2849"
author: "Haotian Wu"
output: html_document
---
```{r}
library(tidyverse)
```

## Problem 1
### Create a data frame
Creating a data frame contains: a random sample of normal distribution, a logical vector, a character vector, and a factor vector. 

```{r}

df <- tibble(
  
  set.seed(10),
  
  ## a random sample of size 10 from a standard Normal distribution
  sample_set = rnorm(10), 
  
  ## a logical vector indicating whether elements of the sample are greater than 0
  log_vec = c(sample_set > 0), 
  
  ## a character vector of length 10
  char_vec = c("This", "is", "a", "character", "vector", "which", "contains", "10", "random", "characters"),
  
  ## a factor vector of length 10, with 3 different factor “levels”
  fac_vec = factor(c("tall", "grande", "venti", "grande", "venti", "grande", "tall", "venti", "grande", "tall"))
  
)

```

### Take the mean of each variable
```{r}
## mean of the random sample of size 10 from a normal distribution
mean(pull(df, 1))

## mean of the logical vector
mean(pull(df, 2))

## mean of the character vector
mean(pull(df, 3))

## mean of the factor vector
mean(pull(df, 4))
```
As the results shown, we can take means of the sample size and the logical vector, but not for for the character vector or the factor vector. 

### Convert variables
Use `as.numeric` function to the logical, character, and factor variables

```{r, eval = FALSE}

## logical vector
as.numeric(pull(df, 2))

## character vector
as.numeric(pull(df, 3))

## factor vector
as.numeric(pull(df, 4))

```

applies the as.numeric function to the logical, character, and factor variables