---
title: "P8105_HW1_hw2849"
author: "Haotian Wu"
output: github_document
---
```{r}
library(tidyverse)
```

## Problem 1
### Create a data frame
Creating a data frame contains: a random sample of normal distribution, a logical vector, a character vector, and a factor vector. 

```{r}

df <- tibble(
  
  set.seed(10),
  
  ## a random sample of size 10 from a standard Normal distribution
  sample_set = rnorm(10), 
  
  ## a logical vector indicating whether elements of the sample are greater than 0
  log_vec = c(sample_set > 0), 
  
  ## a character vector of length 10
  char_vec = c("This", "is", "a", "character", "vector", "which", "contains", "10", "random", "characters"),
  
  ## a factor vector of length 10, with 3 different factor “levels”
  fac_vec = factor(c("tall", "grande", "venti", "grande", "venti", "grande", "tall", "venti", "grande", "tall"))
  
)
df
```

### Take the mean of each variable
```{r}
## mean of the random sample of size 10 from a normal distribution
mean(pull(df, 1))

## mean of the logical vector
mean(pull(df, 2))

## mean of the character vector
mean(pull(df, 3))

## mean of the factor vector
mean(pull(df, 4))
```
As the results shown, we can take means of the sample size and the logical vector, but not for for the character vector or the factor vector. 

### Convert variables
Use `as.numeric` function to the logical, character, and factor variables

```{r, eval = FALSE}

## logical vector
as.numeric(pull(df, 2))

## character vector
as.numeric(pull(df, 3))

## factor vector
as.numeric(pull(df, 4))
```

Apply the as.numeric function to the logical, character, and factor variables. The results return a list of numbers for logical variable and factor variable. It explains there exists a mean for logical variable since it consider `TRUE` as `1` and `FALSE` as `0`, and it returns a mathematical mean for logical vector.

## Problem 2

### A short description of the dataset
```{r}
data("penguins", package = "palmerpenguins")

summary(penguins)
nrow(penguins)
ncol(penguins)
``` 
The size of the dataset is 344 rows and 8 columns. It contains penguins species and their habits, bill length and depth, flipper length, body mass, sex and ages. These penguins contain 165 female penguins and 168 male penguins, born between 2007 and 2009. The mean of flipper length is 200.9. 

### scatter plot
```{r scatter}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm)) + geom_point() + aes(color = species)

ggsave("penguins_scatterplot.pdf")
```